Simulating Benefits, Costs, and Tradeoffs of Spatial Management in Marine Social-Ecological Systems

### 2023-06-05 presentations/tunacamp_slides.qmd
updating lockfile

@@

-   Fast! (fractions of a second for 10x10 system over 20 years with
    quarterly steps)

@@

@@

  - See later releases for age-specific and *advection*

@@

@@

Absent management fleet can either be *constant effort*^[with or without MPA attrition] or *open access*

@@

@@

![](imgs/03_marlin_paper_files/figure-pdf/fig-blue-results-1.png){.absolute top=100 left=200 width="650" height="550"}

## Complexity Matters!

@@

## Of MICE and `marlin`

@@

- MICE models like `marlin` can help illuminate drivers of social-ecological outcomes in fisheries

@@

-   twitter: @danovand0
:::

>>>>

## Time for Models! {background-image="https://c.tenor.com/FtuByrhdiwIAAAAC/monty-python.gif" background-size=contain}

@@

-   Fast! (fractions of a second for 10x10 system over 20 years with
    quarterly steps)
      - R in the front, C++ in the back

- Recursive (you can pass it to itself) for customized applications (e.g. MSE)

@@

- Flexible spawning seasons

- We'll get to movement...
:::
::: {.column width="40%"}

![](imgs/fishy.jpeg)

:::
:::

@@

  - See later releases for age-specific and *advection* (aka oceanography!)

@@

This is the important part

$$ 
\frac{\Delta_{t}}{\Delta_{d}^2}De^{\frac{\Delta_t(H(p2,t,s,a) - H(p1,t,s,a))}{\Delta_d}} 
$$ {#eq-diffusion2}

@@

Conditional on management management fleet can either be *constant effort*^[with or without MPA attrition] or *open access*

@@

::: {.notes}

Fleet One primarily targets the grouper and near-shore snapper populations, but will land
any incidentally captured sharks. Fleet One has a logistic selectivity
pattern for all species, as they retain any fish caught for consumption
or sale. both grouper and shallow-reef snapper due to demand for "plate
sized" fish , and logistic selectivity for sharks, as any shark caught
is retained. Fleet One is totally dependent on fishing for their
livelihood, meaning the local community takes advantage of every
possible opportunity to fish, and as such we model it as a "constant
effort" fishery. Do to having less efficient boats, Fleet One has a
higher cost per distance coefficient than Fleet Two. Fleet One's home
port is located on the site of the grouper spawning aggregation.

Fleet Two is a more commercial fleet that primarily targets the
deep-water snapper population. This fleet primarily sells their catch to
local restaurants and distributors where plate-sized fish are prized,
and so for both snapper and grouper Fleet Two has a dome-shaped
selectivity pattern [@kindsvater2017]. While plate-sized deep snapper
are the primary target of Fleet Two, we model Fleet Two's selectivity
for deep snapper as logistic due to high levels of discard mortality for
deep-water snapper resulting from barotrauma. Fleet Two catches
groupers, though less than Fleet One, and receives no price for sharks
due to the requirements of a certification program through which they
sell their deep-water snapper. Accidental captures (bycatch) of sharks
do occur, which results in mortality. Fleet Two operates under
open-access dynamics, as fishing is not the only means of subsistence
for this community; short-term effort expands and contracts in response
to profitability of the primarily grouper-driven fishery. Fleet two's
home port is located further north from Fleet One.

@@

![](imgs/03_marlin_paper_files/figure-pdf/fig-blue-results-1.png){.absolute top=100 left=200 width="750" height="600"}

## Complexity Matters! (but it's costly)

@@

## Of MICE and `marlin` {.smaller}

@@

- [MICE(ish)](https://research.csiro.au/mice/) models like `marlin` can help illuminate drivers of social-ecological outcomes in fisheries

@@

-   twitter: @danovand0

- website: [danovando.com](https://www.weirdfishes.blog/)
:::
